ABORTO: ¿qué piensan los ecuatorianos?

### 2022-02-22 2020-11-02-los-ecuatorianos-aprueban-el-aborto.Rmd
cambio del color del grafico

```{r, echo=FALSE, fig.pos= "h",fig.align='center', out.width='90%'}
abortion.freq %>% ggplot(aes(x = reorder(levels, 10:1), y = freq)) + geom_bar(stat = "identity", fill = "skyblue") + 
  coord_flip() + geom_text(aes(label= scales::percent(freq, accuracy = 0.1)), hjust=-0.2, size=3, fontface = "italic") + labs(x="", y="", title="Opinión de los ecuatorianos sobre el aborto") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7))  + theme(axis.text=element_text(size=10)) + theme(plot.title = element_text(color="black", size=14, face="bold.italic"))
```

>>>>

```{r, echo=FALSE, fig.pos= "h",fig.align='center', out.width='90%'}
abortion.freq %>% ggplot(aes(x = reorder(levels, 10:1), y = freq)) + geom_bar(stat = "identity", fill = "red") + 
  coord_flip() + geom_text(aes(label= scales::percent(freq, accuracy = 0.1)), hjust=-0.2, size=3, fontface = "italic") + labs(x="", y="", title="Opinión de los ecuatorianos sobre el aborto") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7))  + theme(axis.text=element_text(size=10)) + theme(plot.title = element_text(color="black", size=14, face="bold.italic"))
```
